%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Ocado Limited\\ Freepost 13498\\ PO BOX 3 62\\ Hatfield AL9 7BR} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Dr. Guillaume de Chambrier \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Avenue de la gare 3 \\ 1020 Renens \\ (+41) 79 822 76 35 % Your address and phone number
\end{center} 
\vfill

\signature{Guillaume de Chambrier} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Ms. Markey} 


%it's ok but right now it doesn't look like you spent much time writing it.
%Just in case you didn't notice, the first paragraph is repeated. The official name of the project is SecondHands, 
%written together with capital S, H. In the third paragraph, I don't know what you mean by "the hart of acting under uncertainty", is it art/heart??

%I think you should structure a bit more your skills.

% (1) Say first that you are an expert in mathematical modelling,  machine learning and robotics. 

% (2) Then you talk about you thesis "The essence of my Ph.D thesis lies at the heart? 
%     of acting under uncertainty which will be a valuable skill to contribute to the project." And then you highlight 
%     your experience with many of the numerous robots from LASA, for example with the LWR + F/T sensor.


% (3) They will like you, because they have to integrate the setup and the code from LASA at Ocado, 
%     and you would be perfect for helping there at the beginning and immediately.

%     Best,
%     jose
%--------------------------------------------------------------------------------------------------
%Here is my new propostion :
%check out vacancy for robotics research engineer under :http://www.ocado.jobs/ocado-technology-careers/
%Have you done Java and Unix. If so you can complete the sentence concerning Linux with
%- 
%and I have used Java and Unix in past projects.
%----

I am writing to you having been informed of your vacancy through the robotics-worldwide message group. A Swiss-British national, I have recently obtained my Ph.D doctorate in 
robotics from the Swiss Federal Institute of Technology Lausanne (EPFL) in the LASA robotics laboratory, partner in the SecondHands European project.

My experise lies in Machine Learning (ML), mathematical modelling and robotics. I have both taught cours in Machine Learning (MSc and Ph.D) and  published 
work on new machine learning methods in reinforcement learning and non-parametric Bayesian state space estimation with an emphasis on robotic applications. 
See current examples of my ML activities. (\href{http://chambrierg.com/projects/np_regression/}{non-parametric egression} and \href{http://chambrierg.com/projects/e-pca/}{E-PCA})

My research for the past five years has focused on acting under uncertainty. Using  belief-space planning techniques I have developed and published robotic control 
algorithms which consider state uncertainty during task execution. I  am an expert in   ROS, ros\_control, Moveit for robotic systems and I have strong software expertise 
in C++/Python under Linux. I have developed a ROS package for an ATI force-torque sensor and a KUKA LWR robot (see \href{https://github.com/epfl-lasa/kuka-lwr-ros}{kuka-lwr-ros}), 
and Jos\'{e} Ram\'{o}n Medina, working in the SecondHands project, is currently using my software and he would be happy to give you an appraisal. This framework has been used 
specifically to teach the KUKA to search for and connect an electric power socket without using any visual information in a programming by demonstration 
framework (see \href{http://chambrierg.com/projects/rl_belief_space/}{Reinforcement learning in belief space}). I  have also experience with other robotic 
platforms such as the Barrett WAM Arm, Hand and Allegro Hand and I have contributed a new distance metric to the KDTree of point cloud library.

Ocado is company where I can contribute in a significant way to state-of-the-art robotics research using my knowledge of sensor-guided robotic systems. 
The increasing investment by Ocado in robotic systems and their recognition of the importance of human-robot collaboration makes it an ideal environment. 
I should be most happy to be part of an ambitious robotic company looking to acquire a global presence.

I will be moving to London in January and I am at your disposition at any
time for an interview. You can also visit my personal web-page: \href{www.chambrierg.com}{chambrierg.com}

\closing{Yours sincerely,}



%----------------------------------------------------------------------------------------

\end{letter}

\end{document}\grid
