%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Dr. Guillaume}{de Chambrier}
\address{Avenue de la gare 3, 1020 Renes, Switzerland}
\mobile{(+41) 79 822 76 35} 
%%% Social
\email{chambrierg@gmail.com}
\homepage{www.chambrierg.com}
\github{gpldecha}
\linkedin{guillaume-de-chambrier-57386845}
%%% Optionals
\position{Robotics Research Software Engineer}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Ocado Limited\\ Freepost 13498\\ PO BOX 3 62\\ Hatfield AL9 7BR}
\letterdate{\today}
\lettertitle{Job Application for Robotics Research Software Engineer }
\letteropening{Dear Mr./Ms.,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Claud D. Park~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}

%State the reason for the letter, name the position or type of work you
%are applying for and identify the source from which you learned of the opening (i.e. career
%development center, newspaper, employment service, personal contact).

I am a Swiss-British national and I have recently obtained my Ph.D doctorat in robotics from 
EPFL in the LASA robotics lab  which happens to also be a partnair in the second hands european project.  
I was made aware of your vacancy from the robotics-worldwide message group. 

%\cvparagraph{Why me and Ocado?}

%Indicate why you are interested in the position, the company, its products,
%services - above all, stress what you can do for the employer. If you are a recent graduate,
%explain how your academic background makes you a qualified candidate for the position. If
%you have practical work experience, point out specific achievements or unique qualifications.
%Try not to repeat the same information the reader will find in the resume. Refer the reader to
%the enclosed resume or application which summarizes your qualifications, training, and experiences.
%The purpose of this section is to strengthen your resume by providing details which
%bring your experiences to life.

% Why am I interested in the position,
The increasing investement by Ocado in robotic systems whilst recognising the importance of 
human-robot collaboration makes it an ideal environment for me to contribute. The roles and 
responsibablities outlined in the offer match my competences. During my 
Ph.D I have, for instance, closely worked with force-torque sensor information which I used 
for realtime state estimation. With only force-torque and kinematic information I thought a KUKA LWR 
robot to search for and connect an electric power socket in a programming by demonstration
framework without relying on any visual information. The essence of my Ph.D thesis lies at the 
hart of acting under uncertainty which will be a valuable skill to contribute to the project. 

As a consequence I am very experienced in robotic software developpment (ROS, ros\_control)
and mathematical modelling and machine learning. In terms of libraries, I have worked with and added 
a new distance metric to the KDTree of point cloud library. You may contact José Ramón Medina 
who is currently working on the second hands project and is using the software I developed.

The fact that the position you are offering is long term going behond the Horizon 2020 project 
makes Ocado in par with my ambitions of being part/leading the builind of 
sucessful robotic company with a global outreach. 

% This post is permanent and will persist beyond the duration of the Horizon 2020 projects.
% Participate effectively in investigating and implementing sensor-guided robotics solutions to a wide variety of automation problems
% Perform mathematical modelling and algorithm development to achieve real-time sensor-guided robot motions.
% Contacts in robotics etc...

\cvparagraph{Why Me?}

Request a personal interview and indicate your flexibility as to the
time and place. Repeat your phone number in the letter and offer assistance to help in a
speedy response. For example, state that you will be in the city where the company is located
on a certain date and would like to set up an interview. Alternatively, state that you will call
on a certain date to set up an interview. End the letter by thanking the employer for taking
time to consider your credentials.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
